\section{Methodology}
The parameter space includes varying spatial grid resolutions (\(N_x\)), power indices (\(p\)), regularization parameters (\(\varepsilon\)), simulation stopping times (\(T\)), and Jacobian sparsity utilizations. The left Dirichlet boundary condition is fixed at \(u(t,0) = 1\). For each parameter set, a solution computed via the CVODE method from SUNDIALS with strict relative and absolute error tolerances (\(\texttt{rtol} = \texttt{atol} = 10^{-13}\)) is used as a reference. Solutions are compared via the grid-weighted discrete \(L^2\) norm, defined as
\begin{equation}
  ||\mathbf{e}||_{L^2}=\left(\Delta x \sum |u_i - u_i^{\text{ref}}|^2\right)^{\frac{1}{2}}.
  \end{equation}

  The following metrics are evaluated: computation time, error (compared to CVODE with strict tolerances), function evaluations (nfev), Jacobian evaluations (njev), and matrix decompositions (nlu). In the following sections, we will omit detailed descriptions of nfev, njev, and nlu, and instead focus on the computation time which is easier to grasp.

  The analytical Jacobian matrix was not explicitly provided to any of the tested integrators. The solvers were configured to rely on their internal finite-difference quotient approximations, given only the highly banded (tridiagonal) structural footprint. This constraint reflects out-of-the-box engineering workflows where deriving analytical Jacobians for highly degenerate nonlinear systems is labor-intensive. The performance metrics are intended to capture the effective robustness of each solver's internal step-size and finite-difference heuristics when operating as a black-box integrator.   

The implementation is publicly available on GitHub \footnote{\url{https://github.com/kristian-tichota/p-laplacian-bench}} under the free AGPL-3.0-or-later license. The documentation explains how to replicate the benchmarks in this paper. Similar relative results are to be expected but are not strictly guaranteed due to host architecture differences.

The system specifications are detailed in Table \ref{tab:hardware_specs}.

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.2}
\caption{Benchmark Environment Specifications}
\label{tab:hardware_specs}
\begin{tabularx}{\textwidth}{@{} l >{\raggedright\arraybackslash}X @{}}
\toprule
\textbf{Component} & \textbf{Specification} \\ 
\midrule
CPU & AMD Ryzen 5 5600X (6-Core/12-Thread, @ 4.65 GHz) \\
Memory & 32 GiB System DDR4 RAM \\
OS & Gentoo GNU/Linux x86\_64 (Kernel 6.18.18-gentoo-dist) \\
GCC Compiler Flags & \texttt{-march=native -O2 -pipe} (System/Interpreter only) \\
Python Environment & Python 3.13 \\
Native Libraries & OpenBLAS 0.3.31 and SUNDIALS (via pre-compiled PyPI wheels) \\
\bottomrule
\end{tabularx}
\end{table}
